|

### 2021-05-20 appendix/appendix.Rmd
rewrites result reports from meta regressions

[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:

1. In regard to the estimation method, papers that use `PANEL` data or `RDD`
   designs have smaller effects than articles that employ `OLS` estimations.

2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.

@@

All moderators are insignificant in the meta-regressions of Expenditure as a Percentage of GDP.

@@

Even for all the coefficients, all moderators remain insignificant.

@@

summary(mod)
```
In the restricted model, with only the main coefficients in the selected papers, no moderator has a significant effect. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

@@

1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.

2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.

3. Over time, the reported coefficients have been increasing in size.

4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.

5. All other moderators are insignificant.

>>>>

[^roman]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.

@@

With all coefficients, among the results of the effect sizes on the Log of Expenditure Per Capita Regressions, we find that in regard to the estimation method, papers that use `PANEL` data or `RDD`
   designs have smaller effects than articles that employ `OLS` estimations.

```{r}
# 2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.
```

@@

In the meta-regressions of Expenditure as a Percentage of GDP, we found that:

1. More recent papers find smaller effect sizes than older studies.

2. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.

@@

With all coefficients, the results of the effect sizes on the Expenditure as a Percentage of GDP regressions are the following:

1. Recent papers find even smaller effect sizes than older studies.

2. Studies using non-majoritarian systems find more positive effects between variables.

3. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.

@@

summary(mod)
```
In the restricted model, with only the main coefficients in the selected papers, only Unicameralism has a positive, significant effect. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

@@

1. Coefficients from non-majoritarian systems are significantly smaller than those found in purely majoritarian systems.

2. Compared with `OLS`, `PANEL`, `IV` and `RDD` report significantly smaller coefficients.

3. Evidence from purely unicameral systems produces significantly larger effect sizes.

4. All other moderators are insignificant.

```{r}
#1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.

#2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.

#3. Over time, the reported coefficients have been increasing in size.

#4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.

#5. All other moderators are insignificant.
```
